### 2021-04-21 paper/ase21/abstract.tex
[ASE21] Updating eval
[ASE21] Updated numbers except eval.tex

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  To increase the precision of the type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
  for the recent three years from 2018 to 2021.  $\tool$ took \inred{136.1}
  seconds on average to perform type analysis for each version, and detected
  \inred{177} type-related specification bugs with \inred{52.0}\% precision;
  \inred{92} out of \inred{177} bugs are true bugs.  Among them, \inred{14}
  bugs are newly detected by $\tool$, and the committee confirmed them all.
\end{abstract}

>>>>

  To alleviate the problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using a
  \textit{bug detector}.  For a given specification, $\tool$ first compiles each
  abstract algorithm written in a structured natural language to a corresponding
  function in $\ires$, an untyped intermediate representation for ECMAScript.
  Then, it performs type analysis for compiled functions with specification
  types defined in ECMAScript.  Based on the result of type analysis, $\tool$
  detects specification bugs using a bug detector consisting of four checkers.
  To increase the precision of the type analysis, we present
  \textit{condition-based refinement} for type analysis, which prunes out
  infeasible abstract states using conditions of assertions and branches.  We
  evaluated $\tool$ with all 864 versions in the official ECMAScript repository
  for the recent three years from 2018 to 2021.  $\tool$ took \inred{137.3}
  seconds on average to perform type analysis for each version, and detected
  \inred{161} type-related specification bugs with \inred{56.5}\% precision;
  \inred{91} out of \inred{161} bugs are true bugs.  Among them, \inred{14}
  bugs are newly detected by $\tool$, and the committee confirmed them all.
\end{abstract}

### 2021-04-21 paper/ase21/conclusion.tex
[ASE21] Updated numbers except eval.tex

\section{Conclusion}\label{sec:conclusion}
Since an incorrect description in ECMAScript can lead to the wrong JavaScript
engine implementations, checking the correctness of ECMAScript is essential.
Since ECMAScript is annually released and developed in open process, it becomes
more labor-intensive and error-prone.  To alleviate the problem, we propose
$\tool$, a JavaScript Specification Type Analyzer using Refinement.  It is the
first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  Moreover, to increase
precision of type analysis, we present \textit{condition-based refinement} for
type analysis, which prunes out infeasible abstract states using conditions of
assertions and branches.  We evaluated $\tool$ with all 864 versions in the
official ECMAScript repository for the recent three years from 2018 to 2021.
Our tool took \inred{136.0} seconds on average to perform type analysis for each
version, and detected \inred{177} type-related specification bugs with
\inred{52.0}\% precision; \inred{92} out of \inred{177} bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$, and the committee
confirmed all of them.

>>>>

\section{Conclusion}\label{sec:conclusion}
Since an incorrect description in ECMAScript can lead to the wrong JavaScript
engine implementations, checking the correctness of ECMAScript is essential.
Since ECMAScript is annually released and developed in open process, it becomes
more labor-intensive and error-prone.  To alleviate the problem, we propose
$\tool$, a JavaScript Specification Type Analyzer using Refinement.  It is the
first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  Moreover, to increase
precision of type analysis, we present \textit{condition-based refinement} for
type analysis, which prunes out infeasible abstract states using conditions of
assertions and branches.  We evaluated $\tool$ with all 864 versions in the
official ECMAScript repository for the recent three years from 2018 to 2021.
Our tool took \inred{137.3} seconds on average to perform type analysis for each
version, and detected \inred{161} type-related specification bugs with
\inred{56.5}\% precision; \inred{91} out of \inred{161} bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$, and the committee
confirmed all of them.

### 2021-04-21 paper/ase21/intro.tex
[ASE21] Updating eval
[ASE21] Updated numbers except eval.tex

The main contributions of this paper are as follows:
\begin{itemize}
  \item We present $\tool$, the first tool that performs a \textit{type
    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs such as unknown variables, duplicated variables, missing
    parameters, assertion failures, ill-typed operands, and unchecked
    abrupt completion bugs.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
    precision.  We show that the refinement technique increases the analysis
    precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
    false bugs and detecting \inred{one} more true bug.
  \item We demonstrate the practicality of $\tool$. It takes \inred{136.1}
    seconds on average to perform a type analysis for each version of ECMAScript and detected
    \inred{177} type-related specification bugs with \inred{52.0}\% precision;
    \inred{92} out of \inred{177} bugs are true bugs.  Among them, $\tool$ 
    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
\end{itemize}

>>>>

The main contributions of this paper are as follows:
\begin{itemize}
  \item We present $\tool$, the first tool that performs a \textit{type
    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs such as unknown variables, duplicated variables, missing
    parameters, assertion failures, ill-typed operands, and unchecked
    abrupt completion bugs.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
    precision.  We show that the refinement technique increases the analysis
    precision from \inred{31.8}\% to \inred{56.5}\% by removing \inred{122}
    false bugs and detecting \inred{one} more true bug.
  \item We demonstrate the practicality of $\tool$. It takes \inred{137.3}
    seconds on average to perform a type analysis for each version of ECMAScript and detected
    \inred{161} type-related specification bugs with \inred{56.5}\% precision;
    \inred{91} out of \inred{161} bugs are true bugs.  Among them, $\tool$
    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
\end{itemize}
